MATH 3610 - Project \#1

### 2015-10-01 proj1.tex
still many untracked files, it shouldn't compile

@@

\begin{thebibliography}{9}
\bibitem{areconnect}
	\url{http://ithaca.areaconnect.com/statistics.htm}
\bibitem{CIC}
	\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
\bibitem{walph}
	Wolfram Research Inc.,
	\emph{WolframAlpha},
	Retrieved September 26, 2015
	\url{http://www.wolframalpha.com/input/?i=\%E2\%88\%AB+e\^\%28-a+x\^2+\%2B+b+x\%29+dx}
	\url{http://www.wolframalpha.com/input/?i=ds\%2Fdt+\%3D+r+s+\%28K+-+s+-+a+t\%29}
\end{thebibliography}

>>>>

\subsection{Improved Model}

In the preceding model, once people became infected, they stayed
	infected for the duration of the run.
The following model adds a parameter, the ``curing rate'' $\gamma$,
	which represents the rate at which individuals in the sick population
	recover (and join the removed population).
This model is the SIR model, and has standard parameters:

\begin{align*}
\frac{dI}{dt} & = \frac{ \beta S I}{N} - \gamma I\\
\frac{dS}{dt} & = -\frac{\beta S I}{N} - r_v \\
\frac{dR}{dt} & = r_v + \gamma I 
\end{align*}

We can use this model for pareto optimization.
Cornell's population is about 21,000 \cite{cornellpop},
	while ithaca's population is about 30,000 \cite{census}.
Given a rate of vaccine distribution, by integrating the equations
	we can determine how many total infections there are.
If we had 4000 vaccinations to distribute, we can make a pareto
	curve by plotting the set of points corresponding to different
	relative distributions of the vaccinations.

If one of the populations vaccinates all of its seceptible individuals
	before the other, we need to decide what to do with the vaccines
	that it is not consuming.
If we choose not to redistribute them, the pareto curve looks like this:

\includegraphics[width=0.5\textwidth]{figures/sir-pareto.pdf}

If we choose to redistribute them, for $\beta = 6$ and $\gamma = 4$,
	the curve looks like this:

\includegraphics[width=0.5\textwidth]{figures/sir-pareto-top.pdf}

And the pareto curve looks like:

\includegraphics[width=0.5\textwidth]{figures/sir-pareto-top-pareto.pdf}

We conclude that making sure that all of the vaccines are allocated is very
	important for any vaccine model, noting the difference.
The pareto-optimal points are when 71-84\% of the vaccine goes to the
	cornellians and 29-16\% goes to the ithacans, 
	and when 15-20\% of the vaccine goes to the cornellians 
	and 80-85\% of the vaccine goes to the ithacans.

@@

\begin{thebibliography}{9}
\bibitem{areconnect}
	\url{http://ithaca.areaconnect.com/statistics.htm}
\bibitem{CIC}
	\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
\bibitem{walph}
	Wolfram Research Inc.,
	\emph{WolframAlpha},
	Retrieved September 26, 2015
	\url{http://www.wolframalpha.com/input/?i=\%E2\%88\%AB+e\^\%28-a+x\^2+\%2B+b+x\%29+dx}
	\url{http://www.wolframalpha.com/input/?i=ds\%2Fdt+\%3D+r+s+\%28K+-+s+-+a+t\%29}
\bibitem{census}
	http://quickfacts.census.gov/qfd/states/36/3638077.html
\bibitem{cornellpop}
	https://www.cornell.edu/about/facts.cfm
\end{thebibliography}
